### 2024-02-16 README.Rmd
* `el_pairwise()` and its associated methods are removed.

<!-- badges: start -->
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R-CMD-check](https://github.com/ropensci/melt/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/ropensci/melt/actions/workflows/check-standard.yaml)
[![Codecov test coverage](https://codecov.io/gh/ropensci/melt/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/melt?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
[![runiverse](https://ropensci.r-universe.dev/badges/melt)](http://ropensci.r-universe.dev/ui/#package:melt)
[![ropensci review](https://badges.ropensci.org/550_status.svg)](https://github.com/ropensci/software-review/issues/550)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R-CMD-check](https://github.com/ropensci/melt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/melt/actions/workflows/R-CMD-check.yaml)
[![pkgcheck](https://github.com/ropensci/melt/workflows/pkgcheck/badge.svg)](https://github.com/ropensci/melt/actions?query=workflow%3Apkgcheck)
[![Codecov test coverage](https://codecov.io/gh/ropensci/melt/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/melt?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
[![runiverse](https://ropensci.r-universe.dev/badges/melt)](http://ropensci.r-universe.dev/ui/#package:melt)
[![ropensci review](https://badges.ropensci.org/550_status.svg)](https://github.com/ropensci/software-review/issues/550)

<!-- badges: end -->
